### 2022-01-21 article.tex
Rename Reduce to ReduceAxes
(Ab)Using Implicits conclusion

Type-level programming is becoming more and more popular in the realm of functional programming.
However, the combination of type-level programming and subtyping remains largely unexplored in practical programming languages.
This chapter presents \emph{match types}, a type-level equivalent of pattern matching.
Match types integrate seamlessly into programming languages with subtyping and, despite their simplicity, offer significant additional expressiveness.
We formalize the feature of match types in a calculus based on \SystemFsub and prove its soundness.
We practically evaluate our system by implementing match types in the Scala 3 reference compiler, thus making type-level programming readily available to a broad audience of programmers.

@@

This behavior is more complex than the previous examples, but can still be described accurately by a match type.
We use a match type called |Reduce| to compute the return shape of the operation.

>>>>

@@

This behavior is more complex than the previous examples, but can still be described accurately by a match type.
We use a match type called |ReduceAxes| to compute the return shape of the operation.
